---
title: "IRI analysis"
author: "Andrew Heiss"
date: "`r format(Sys.time(), '%B %e, %Y')`"
output: 
  html_document: 
    css: ../html/fixes.css
    code_folding: hide
    toc: yes
    toc_float: true
    toc_depth: 4
    highlight: pygments
    theme: cosmo
    self_contained: no
    includes:
      after_body: ../html/add_home_link.html
bibliography: /Users/andrew/Dropbox/Readings/Papers.bib
csl: /Users/andrew/.pandoc/csl/american-political-science-association.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, fig.retina=2,
                      tidy.opts=list(width.cutoff=140),  # For code
                      options(width=140))  # For output

library(tidyverse)
library(ggforce)
library(jsonlite)
library(forcats)
library(countrycode)
library(rgdal)

source(file.path(PROJHOME, "Analysis", "lib", "graphic_functions.R"))
```

## Budget and staff over time

```{r budget-staff, message=FALSE}
# Yay GuideStar!
# https://www.guidestar.org/profile/52-1340267
iri.budget <- read_csv(file.path(PROJHOME, "Data", 
                                 "data_base", "iri_budget.csv")) %>%
  mutate(gov_percent = Government / Income)

iri.budget.long <- iri.budget %>%
  select(Year, Income, Expenses, Staff) %>%
  gather(key, value, -Year) %>%
  mutate(type = ifelse(key == "Staff", "Staff", "Budget"))

plot.budget <- ggplot(filter(iri.budget.long, type == "Budget"),
                      aes(x=Year, y=value, colour=key)) +
  geom_line(size=1) +
  labs(x=NULL, y="Reported amount") +
  scale_y_continuous(labels=scales::dollar_format(),
                     limits=c(0, NA)) +
  scale_color_manual(values=ath.palette("palette1")[3:4], name=NULL) +
  theme_ath()

plot.gov <- ggplot(iri.budget, aes(x=Year, y=gov_percent)) +
  geom_line(size=1, colour="#FF4136") +
  labs(x=NULL, y="Percent of income from\ngovernment grants") +
  scale_y_continuous(labels=scales::percent) +
  expand_limits(y=0) +
  theme_ath()

plot.staff <- ggplot(filter(iri.budget.long, type == "Staff"),
                     aes(x=Year, y=value)) +
  geom_line(size=1) +
  labs(x=NULL, y="Full time\nemployees") +
  expand_limits(y=0) +
  theme_ath()

plot.all <- rbind(ggplotGrob(plot.budget),
                  ggplotGrob(plot.gov),
                  ggplotGrob(plot.staff))

panels <- plot.all$layout$t[grep("panel", plot.all$layout$name)]
plot.all$heights[panels] <- unit(c(1, 0.5, 0.5), "null")

grid::grid.newpage()
grid::grid.draw(plot.all)

fig.save.cairo(plot.all, filename="5-iri-budget-staff", 
               width=4.5, height=3.5)
```

```{r results="asis"}
iri.budget %>%
  mutate(Surplus = Income - Expenses) %>%
  pander::pandoc.table()
```

Average income per year: `r iri.budget$Income %>% mean() %>% scales::dollar()`

## Program locations

```{r program-locations, message=FALSE, warning=FALSE}
# Load Robinson map projection
countries.ggmap <- readRDS(file.path(PROJHOME, "Data", "data_processed",
                                     "countries110_robinson_ggmap.rds"))

possible.countries <- data_frame(id = unique(as.character(countries.ggmap$id)))

# IRI has an interactive map of all the countries it works in at 
# http://test-iri.pantheon.io/iri-around-world. It uses jvectormap to display data 
# from a JSON file at http://test-iri.pantheon.io/feeds/countries_interactive_map
# So, I downloaded that and parse it here.
iri.countries.raw <- fromJSON(file.path(PROJHOME, "Data", 
                                       "data_base", "iri_countries.json"))

iri.countries <- iri.countries.raw$countries$country %>%
  mutate(country.name = countrycode(field_country_code, "iso2c", "country.name"),
         iso3 = countrycode(field_country_code, "iso2c", "iso3c"))

countries.to.plot <- possible.countries %>%
  left_join(iri.countries, by=c("id" = "iso3")) %>%
  replace_na(list(field_bool_current_program = 2)) %>%
  mutate(presence = factor(field_bool_current_program, levels=c(1, 0, 2),
                           labels=c("Programs in 2017", "Past programs", "No programming"),
                           ordered=TRUE))

plot.iri <- ggplot(countries.to.plot) +
  geom_map(aes(map_id=id, fill=presence), map=countries.ggmap, 
           size=0.15, colour="black") + 
  expand_limits(x=countries.ggmap$long, y=countries.ggmap$lat) +
  coord_equal() +
  scale_fill_manual(values=c("#FF4136", "grey50", "white")) +
  scale_radius(range=c(0.5, 3.5)) +
  guides(size=guide_legend(nrow=1, order=0, title="Number of award recipients:"),
         fill=guide_legend(order=1, title=NULL)) +
  theme_ath_map() + theme(legend.position="bottom",
                          legend.key.size=unit(0.65, "lines"))
plot.iri

fig.save.cairo(plot.iri, filename="5-iri-work", 
               width=5.5, height=3)
```

Number of countries it works in in 2017: `r filter(iri.countries, field_bool_current_program == "1") %>% nrow()`

## Expenses by region

```{r regional-expenses, message=FALSE, warning=FALSE}
iri.regional <- read_csv(file.path(PROJHOME, "Data", "data_base",
                                   "iri_budget_regions.csv")) %>%
  # Collapse regions:
  # North, Central, and South America go together (since North America is just Mexico)
  mutate(region.collapsed = recode(region,
                                   `North America` = "Central and South America",
                                   `South America` = "Central and South America",
                                   `Central America and the Caribbean` 
                                   = "Central and South America",
                                   `South Asia` = "South and Central Asia",
                                   `Europe` = "Europe (includes Russia)",
                                   `Russia and neighboring states` = "Europe (includes Russia)"))

iri.regions.total <- iri.regional %>%
  group_by(year_end, region.collapsed) %>%
  summarise(expenditures = sum(expenditures)) %>%
  arrange(desc(expenditures)) %>%
  ungroup() %>%
  mutate(crackdown = case_when(
    .$region.collapsed == "Middle East and North Africa" ~ 2011L,
    .$region.collapsed == "Europe (includes Russia)" ~ 2012L,
    TRUE ~ NA_integer_
  )) %>%
  mutate(region.collapsed = fct_inorder(region.collapsed))

plot.iri.regions <- ggplot(iri.regions.total, aes(x=year_end, y=expenditures)) +
  geom_vline(aes(xintercept=crackdown), size=0.5, colour="grey75", linetype="dashed") +
  # geom_vline(xintercept=2011, size=0.5, colour="grey75", linetype="dashed") +
  geom_line(size=1) +
  labs(x=NULL, y="Expenditures") +
  scale_y_continuous(labels=scales::dollar_format()) +
  scale_color_manual(values=ath.palette("palette1"), name=NULL, guide=FALSE) +
  theme_ath() + theme(strip.text=element_text(size=rel(0.8)),
                      strip.background=element_rect(fill="grey90")) +
  facet_wrap(~ region.collapsed)
plot.iri.regions

fig.save.cairo(plot.iri.regions, filename="5-iri-expenditures-region", 
               width=5.5, height=2.5)
```

```{r iri2010-me}
iri.2010 <- tribble(
  ~grant, ~number, ~amount,
  "Iraqi Governance, Civil Society, and Political Party Programs", "DOS S-LMAQM-07-GR-209 6495", 12815842,
  "Iraq Post-Election Initiatives", "DOS S-LMAQM-10-GR-535 6984", 5660233
)
```

2010 is wonky in the Middle East, but that's because they got some massive grants in Iraq, like `r iri.2010$amount %>% sum() %>% scales::dollar()`—the "largest grant ever managed by IRI" [@iri:2009, 2].

```{r results="asis"}
iri.2010 %>% pander::pandoc.table()
```

## Staff and offices by region

```{r staff-offices-region, warning=FALSE}
iri.regional.offices <- iri.regional %>%
  gather(key, value, offices, employees) %>%
  filter(!is.na(value)) %>%
  group_by(year_end, region.collapsed, key) %>%
  summarise(total = sum(value)) %>%
  mutate(key = factor(key, levels=c("offices", "employees"), ordered=TRUE)) %>%
  mutate(key = fct_recode(key, 
                          `Field offices` = "offices",
                          `Employees in field` = "employees")) %>%
  ungroup() %>%
  mutate(crackdown = case_when(
    .$region.collapsed == "Middle East and North Africa" ~ 2011L,
    .$region.collapsed == "Europe (includes Russia)" ~ 2012L,
    TRUE ~ NA_integer_
  ))

plot.iri.regional.offices.all <- ggplot(iri.regional.offices, 
                                        aes(x=year_end, y=total)) +
  geom_vline(aes(xintercept=crackdown), size=0.5, colour="grey75", linetype="dashed") +
  geom_line(size=1) +
  labs(x=NULL, y=NULL) +
  scale_color_manual(values=ath.palette("palette1"), name=NULL) +
  theme_ath() + theme(strip.background=element_rect(fill="grey90"),
                      strip.text=element_text(size=rel(0.8)))

plot.iri.regional.offices.page1 <- plot.iri.regional.offices.all +
  facet_grid_paginate(key ~ region.collapsed, scales="free_y", 
                      switch="y", ncol=3, nrow=2, page=1)

plot.iri.regional.offices.page2 <- plot.iri.regional.offices.all +
  facet_grid_paginate(key ~ region.collapsed, scales="free_y", 
                      switch="y", ncol=3, nrow=2, page=2)

plot.iri.regional.offices.page1
plot.iri.regional.offices.page2

fig.save.cairo(plot.iri.regional.offices.page1, filename="5-iri-regional-staff-page1", 
               width=5.5, height=2.5)
fig.save.cairo(plot.iri.regional.offices.page2, filename="5-iri-regional-staff-page2", 
               width=5.5, height=2.5)
```

## Total number of field offices and employees

```{r total-field-offices, results="asis"}
total.offices <- iri.regional.offices %>%
  group_by(key, year_end) %>%
  summarise(total = sum(total)) %>%
  spread(key, total)

total.offices %>% pander::pandoc.table()
```

## References
