---
title: "Free responses"
author: "Andrew Heiss"
date: '`r format(Sys.time(), "%F")`'
output:
  html_document:
    code_folding: hide
    css: ../html/fixes.css
    highlight: pygments
    includes:
      after_body: ../html/add_home_link.html
    self_contained: no
    theme: cosmo
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    highlight: pygments
    includes:
      in_header: ../TeX/top_stuff.tex
    latex_engine: xelatex
    toc: yes
    toc_depth: 3
mainfont: Source Sans Pro
fontsize: 10pt
...

```{r load-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(stringr)
library(pander)

# Load cleaned, country-based survey data (*with* the Q4\* loop)
survey.clean.all <- readRDS(file.path(PROJHOME, "Data", "data_processed", 
                                      "survey_clean_all.rds"))

# Load cleaned, organization-based data (without the Q4 loop)
survey.orgs.clean <- readRDS(file.path(PROJHOME, "Data", "data_processed", 
                                       "survey_orgs_clean.rds"))

org.free.responses <- survey.orgs.clean %>%
  arrange(clean.id) %>%
  rowwise() %>%
  mutate(preface = str_interp("${clean.id}; HQ: ${Q2.2_country}"))
  # mutate(preface = str_interp("${Q2.1} (${clean.id}); HQ: ${Q2.2_country}"))

country.free.responses <- survey.clean.all %>%
  arrange(clean.id) %>%
  rowwise() %>%
  mutate(preface = str_interp("${clean.id}; HQ: ${Q2.2_country}; target: ${Q4.1_name}"))
  # mutate(preface = str_interp("${Q2.1} (${clean.id}); HQ: ${Q2.2_country}; target: ${Q4.1_name}"))

pandoc.definition <- function(term, definition) {
  template <- "${term}
  
:   ${definition}"
  
  str_interp(template, list(term=term, definition=definition))
}

print.answer.list <- function(df, question) {
  output <- df %>%
    rename_(.dots=setNames(list(question), "question")) %>%
    filter(!is.na(question)) %>%
    rowwise() %>%
    mutate(output = pandoc.definition(preface, question),
           output = str_replace_all(output, "\\\\(\\w)", "\\\\ \\1"))
  cat(output$output, sep="\n\n")
  
  # str_replace_all(bloop$Q3.9, "\\\\(\\w)", "\\\\ \\1")
  # 
  bloop <- country.free.responses %>%
    filter(clean.id == 1437)
  bloop$Q4.10
}
```

## Organizational questions

### *Q3.9*: In general, what would you say your organization is trying to accomplish?

```{r q3-9, results="asis"}
print.answer.list(org.free.responses, "Q3.9")
```

### *Q3.10*: How is your organization's mission, vision, and values reflected in these objectives?

```{r q3-10, results="asis"}
print.answer.list(org.free.responses, "Q3.10")
```

### *Q3.11*: Have these objectives changed at all in the last 10 years? If so, how?

```{r q3-11, results="asis"}
print.answer.list(org.free.responses, "Q3.11")
```

### *Q3.12*: What are the major obstacles, if any, to reaching your organization's objectives?

```{r q3-12, results="asis"}
print.answer.list(org.free.responses, "Q3.12")
```

### *Q3.13*: Are there any changes that you would like to see in your organization's goals and strategies, now or in the future?

```{r q3-13, results="asis"}
print.answer.list(org.free.responses, "Q3.13")
```

## Contact with government

### *Q4.10*: How is the government of `target_country` involved in your work?

```{r q4-10, results="asis"}
print.answer.list(country.free.responses, "Q4.10")
```

## NGO regulations and restrictions

### *Q4.16a*: Regulations regarding registration

```{r q4-16a, results="asis"}
print.answer.list(country.free.responses, "Q4.16_registration_TEXT")
```

### *Q4.16b*: Regulations regarding operations

```{r q4-16b, results="asis"}
print.answer.list(country.free.responses, "Q4.16_operations_TEXT")
```

### *Q4.16c*: Regulations regarding speech and advocacy

```{r q4-16c, results="asis"}
print.answer.list(country.free.responses, "Q4.16_speech_TEXT")
```

### *Q4.16d*: Regulations regarding communication and cooperation

```{r q4-16d, results="asis"}
print.answer.list(country.free.responses, "Q4.16_communications_TEXT")
```

### *Q4.16e*: Regulations regarding assembly

```{r q4-16e, results="asis"}
print.answer.list(country.free.responses, "Q4.16_assembly_TEXT")
```

### *Q4.16f*: Regulations regarding resources

```{r q4-16f, results="asis"}
print.answer.list(country.free.responses, "Q4.16_resources_TEXT")
```

### *Q4.18*: How do the local laws and regulations in `target_country` affect your organization's ability to pursue its mission?

```{r q4-18, results="asis"}
print.answer.list(country.free.responses, "Q4.18")
```

## Responses to regulations

### *Q4.20*: How has your organization's mix of programming changed in `target_country`?

```{r q4-20, results="asis"}
print.answer.list(country.free.responses, "Q4.20")
```

### *Q4.21a*: How org changed its funding sources

```{r q4-21a, results="asis"}
print.answer.list(country.free.responses, "Q4.21_funding_TEXT")
```

### *Q4.21b*: How org changed which issues it works on

```{r q4-21b, results="asis"}
print.answer.list(country.free.responses, "Q4.21_issues_TEXT")
```

### *Q4.21c*: How org changed how it communicates with the government

```{r q4-21c, results="asis"}
print.answer.list(country.free.responses, "Q4.21_comm_govt_TEXT")
```

### *Q4.21d*: How org changed how it communicates with donors

```{r q4-21d, results="asis"}
print.answer.list(country.free.responses, "Q4.21_comm_donors_TEXT")
```

### *Q4.21e*: How org changed the locations it works in

```{r q4-21e, results="asis"}
print.answer.list(country.free.responses, "Q4.21_locations_TEXT")
```

### *Q4.21f*: How org changed the location of its country office

```{r q4-21f, results="asis"}
print.answer.list(country.free.responses, "Q4.21_country_office_TEXT")
```

### *Q4.21g*: How org used more local staff or volunteers

```{r q4-21g, results="asis"}
print.answer.list(country.free.responses, "Q4.21_local_staff_TEXT")
```

### *Q4.21h*: How org used more foreign staff or volunteers

```{r q4-21h, results="asis"}
print.answer.list(country.free.responses, "Q4.21_foreign_staff_TEXT")
```

## Final questions

### *Q5.1*: Do you have any additional comments?

```{r q5-1, results="asis"}
print.answer.list(org.free.responses, "Q5.1")
```
